### 2021-06-25 src/paper/report.tex
Add comments by Philipp Eisenhauer.

Since early 2020,\comment[id=J]{Put stronger focus on time dependent rapid test
sensitivity (30\% before day of onset of infectiousness)} the CoViD-19 pandemic has
presented an enormous challenge to humanity on many dimensions. The development of
highly effective vaccines holds the promise of containment in the medium term. However,
most countries find themselves many months---and often years---away from reaching
vaccination-induced herd immunity \citep{Swaminathan2021}.\comment[id=HM]{Need to find
some more scientific citation before submission} In the meantime, it is of utmost
importance to employ an effective mix of strategies for containing the virus. The most
frequent initial response was a set of non-pharmaceutical interventions (NPIs) to reduce
contacts between individuals. While this has allowed some countries to sustain
equilibria with very low infection numbers,\footnote{See \citet{Contreras2021} for a
theoretical equilibrium at low case numbers which is sustained with
test-trace-and-isolate policies.} most have seen large fluctuations of infection rates
over time. Containment measures have become increasingly diverse and now include rapid
testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the
influence of seasonal patterns or of more infectious virus strains are well understood
in quantitative terms.

>>>>

Since early 2020,\comment[id=J]{Put stronger focus on time dependent rapid test
sensitivity (30\% before day of onset of infectiousness)} the CoViD-19 pandemic has
presented an enormous challenge to humanity on many dimensions. The development of
highly effective vaccines holds the promise of containment in the medium term. However,
most countries find themselves many months---and often years---away from reaching
vaccination-induced herd immunity \citep{Swaminathan2021}.\comment[id=HM]{Need to find
some more scientific citation before submission} In the meantime, it is of utmost
importance to employ an effective mix of strategies for containing the virus. The most
frequent initial response was a set of non-pharmaceutical interventions (NPIs) to reduce
contacts between individuals. While this has allowed some countries to sustain
equilibria with very low infection numbers,\footnote{See \citet{Contreras2021} for a
theoretical equilibrium at low case numbers which is sustained with
test-trace-and-isolate policies.} most have seen large fluctuations of infection rates
over time. Containment measures have become increasingly diverse and now include rapid
testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the
influence of seasonal patterns or of more infectious virus strains are well understood
in quantitative terms.\comment[id=K]{feedback from Philipp:
\begin{itemize}
    \item he would suggest to lay more focus on explaining the mechanisms behind our
    results
    \item he suggests we should try to get some form of confidence bands or standard errors
    \item he got the wrong impression that we only have three mechanisms and that the
    rapid tests are the residual.
\end{itemize}
}
